Title

### 2016-11-24 paper.tex
typos

In this paper we focus on graphs, i.e. we consider each example to be a different graph.
A graph is a tuple $G=(V_G,E_G,L_G)$, where $V_G=\{v_1,\ldots,v_n\}$ is the set of vertices, $E_G=\{(u,v) | u,v \in V_G\}$ is the set of edges (with $|E_G|=m$), and $L_G: V_G \rightarrow \Sigma$ is a function mapping each vertex to a discrete label in a fixed alphabet $\Sigma$.
A graph is undirected if $(u,v)\in E_g \Rightarrow (v,u) \in E_G$, otherwise it is directed.
In this setting, there are several graph kernels defined in literature based on random walks~\cite{Kashima03marginalizedkernels,Mahe2004} ($O(n^3)$ computational complexity), shortest paths~\cite{Kriegel05shortestpath} ($O(n^4)$ computational complexity), subgraphs up to a fixed size $h$~\cite{Shervashidze2009} ($O(n^h)$ complexity). The problem with these kernels is the high computational complexity, that makes them inapplicable to several real-world datasets.
Recently, different almost linear time graph kernels have been defined in literature \cite{Heinonen2009,NIPS2009_0533,Costa2010,Shervashidze2011,Dasan2012,DaSanMartino2016}, and these are the ones we focus on in this paper.
In the following we will give some details about the considered alternatives.
Each kernel restricts to specific kinds of subgraphs, up to a certain dimension (that, in general, is a kernel parameter).
Note that it is out of the scope of this paper to give an extensive comparison among the various graph kernels.

The Weisfeiler-Lehman Fast Subtree kernel (WL)~\cite{NIPS2009_0533}  counts the number of identical subtree patterns obtained by subtree-walks up to height $h$ in the two input graphs. The complexity of the kernel is $O(|E|h)$. 
While being fast to compute, the kernel may lack of expressiveness for some tasks given that the number of non-zero features generated by one graph is at most $|V|h$. 
Note that the subtree-walks extracted by the kernel differ from  subtree structures because a node can appear multiple times in the same subtree-walk.

@@

The Ordered Decomposition DAGs kernel framework (ODD)~\cite{Dasan2012} considers as non-zero features in the RKHS the trees that appear as subtrees of the input graphs.
It exploits the shortest-path (up to length $\eta$) DAG decompositions starting from each node in the graph to generate DAG structures, and then extracts tree features from them.
Each tree-feature is weighted as $f \cdot \lambda^{dim}$, where $f$ is the frequency of the feature, $dim$ its dimension (the number of vertices in the tree) and $\lambda>0$ a weighting parameter.
The time complexity of the main representative of this family, ODD$_{ST}$, is, under mild conditions, $O(|V_G| \log |V_G|)$, and the number of generated features for a graph is at most $|V_G|\rho^\eta$.

@@

\section{Our framework}
Often, to work well MKL algorithms require an high number of kernels, and when we use structured data as input, such as graphs, the computational effort to calculate each of them can be expensive. Moreover each kernel requires an amount of memory that depends on the number of samples, making the MKL approach unpractical when the number of samples and the number of kernels are huge.
In order to avoid this problem, we propose a method to reduce the number of kernels, based on the robustness of combination vector $\eta$.\\
In particular if $\eta$, the combination vector learned using the whole set of data and all kernel functions, is similar to the weights vector $\eta_s$ learned using the same kernels calculated on a subset of data, then we can use directly $\eta_s$ in our model.
In this way we can learn quickly the kernels combination, but we have to calculate all kernels anyway.
Furthermore, we can use values in $\eta_s$ to perform a ranking over kernels, removing those below a threshold.
Then we fit the model using only the top kernels selected.

>>>>

In this paper we focus on graphs, i.e. we consider each example to be a different graph.
A graph is a tuple $G=(V_G,E_G,L_G)$, where $V_G=\{v_1,\ldots,v_n\}$ is the set of vertices, $E_G=\{(u,v) | u,v \in V_G\}$ is the set of edges (with $|E_G|=m$), and $L_G: V_G \rightarrow \Sigma$ is a function mapping each vertex to a discrete label in a fixed alphabet $\Sigma$.
%A graph is undirected if $(u,v)\in E_g \Rightarrow (v,u) \in E_G$, otherwise it is directed.
In this setting, there are several graph kernels defined in literature based on random walks~\cite{Kashima03marginalizedkernels,Mahe2004} ($O(n^3)$ computational complexity), shortest paths~\cite{Kriegel05shortestpath} ($O(n^4)$ computational complexity), subgraphs up to a fixed size $h$~\cite{Shervashidze2009} ($O(n^h)$ complexity). The problem with these kernels is the high computational complexity, that makes them inapplicable to several real-world datasets.
Recently, different almost linear time graph kernels have been defined in literature \cite{Heinonen2009,NIPS2009_0533,Costa2010,Shervashidze2011,Dasan2012,DaSanMartino2016}, and these are the ones we focus on in this paper.
In the following we will give some details about the considered alternatives.
Each kernel restricts to specific kinds of subgraphs, up to a certain dimension (that, in general, is a kernel parameter).
Note that it is out of the scope of this paper to give an extensive comparison among the various graph kernels.

The Weisfeiler-Lehman Fast Subtree kernel (WL)~\cite{NIPS2009_0533}  counts the number of identical subtree patterns obtained by subtree-walks up to height $h$ in the two input graphs. The complexity of the kernel is $O(|E|h)$. 
%While being fast to compute, the kernel may lack of expressiveness for some tasks given that the number of non-zero features generated by one graph is at most $|V|h$. 
Note that the subtree-walks extracted by the kernel differ from  subtree structures because a node can appear multiple times in the same subtree-walk.

@@

The Ordered Decomposition DAGs kernel framework (ODD)~\cite{Dasan2012} considers as non-zero features in the RKHS the trees that appear as subtrees of the input graphs.
It exploits the shortest-path (up to length $\eta$) DAG decompositions starting from each node in the graph to generate DAG structures, and then extracts tree features from them.
Each tree-feature is weighted as $f \cdot \lambda^{dim}$, where $f$ is the frequency of the feature, $dim$ its dimension (the number of vertices in the tree) and $\lambda>0$ a weighting parameter.
The time complexity of the main representative of this family, ODD$_{ST}$, is, under mild conditions, $O(|V_G| \log |V_G|)$.%, and the number of generated features for a graph is at most $|V_G|\rho^\eta$.

@@

\section{Proposed framework}
Often, to work well MKL algorithms require an high number of kernels, and when we use structured data as input, such as graphs, the computational effort to calculate each of them can be high. Moreover each kernel requires an amount of memory that depends on the number of samples, making the MKL approach unpractical when the number of samples and the number of kernels are huge.
In order to avoid these problems, we propose a method to reduce the number of kernels to compute on the complete dataset, based on the robustness of the combination vector $\boldsymbol{\eta}$ when considering just a subset of the available data.\\
In particular if $\boldsymbol{\eta}$, the combination vector learned using the whole set of data and all kernel functions, is similar to the weights vector $\eta_s$ learned using the same kernels calculated on a subset of data, then we can use directly $\eta_s$ in our model.
In this way we can learn quickly the kernels combination, but we have to calculate all kernels anyway.
Furthermore, we can use values in $\eta_s$ to perform a ranking over kernels, removing those below a threshold.
Then we fit the model using only the top kernels selected.
